Risk Perceptions for Wearable Devices

### 2015-02-25 tex-inputs/intro.tex
more hashing out of introduction and scoping

@@

%% LL: worked upto here. below is rough.

{\color {red} WORKED UPTO HERE BELOW IS ROUGH}

@@

Although Google Glass was most iconic wearable of its time, it has since disappeared due to complaints from the public\cite{13_google_2015}. No formal statement from Google addresses the states that the reason for its disappearance is due to negative social pressures. However, most suspect that this is the reason for its disappearance, rather than a shift in interest. One popular tech magazine called glass the ``straw the broke the back of the privacy camel's back \cite{14_dvorak_2014}''. The wearable device was not acceptable to the public at large, making bystanders feel uncomfortable with the possibility of recording personal details, conversations, and photos. Many instances of assault \cite{1_russell_2014, 15_mashable_2014, 16_gross_2014} on wearers were also reported, resulting from a combination of privacy invasion and social tension\footnote{Google has come to represent gentrification in San Francisco ... [which] makes wearable device owners look and sound like one of the people whom residents of the city have come to feel oppressed by \cite{17_matyszczyk_2014}. The term ``Glasshole'' \cite{18_google_2015} has been defined specifically to refer to Google glass wearers.} . The public was generally unsympathetic to the situation, tweets including, ``I'm going to shove your pathetic nerd body into a locker,'' ``Nothing radicalizes you like having [your] home taken from you. Gentrification at this [point] feels like destruction of property,'' and``As far as your 'hate crime' allegation is concerned, Entitled Tech Trash isn't a protected class just yet'' \cite{1_russell_2014,15_mashable_2014}.

{\color {red} This calls for privacy research in this area! It's more important than ever! Or something along those lines.}  To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}. A better understanding of users' risk perceptions will enable researchers and companies to focus on users' concerns. The goal of this paper is to gain a better sense of what those concerns are.  {\color {red} "there has been extensive work on the need for showing users how certaind data is being captured so that they can have more control.. now we have wearables, and collect more data types. We have an issue of showing everyone everything all the time, since attention is a finite resources. We need to identify situations that people want to warn them about, and transparently access things that they are benign."}

>>>>

%!TEX root = ../paper.tex

@@

@@

Although Google Glass was most iconic wearable of its time, it has since disappeared due to complaints from the public\cite{13_google_2015}. No formal statement from Google addresses the states that the reason for its disappearance is due to negative social pressures. However, most suspect that this is the reason for its disappearance, rather than a shift in interest. One popular tech magazine called glass the ``straw the broke the back of the privacy camel's back \cite{14_dvorak_2014}''. The wearable device was not acceptable to the public at large, making bystanders feel uncomfortable with the possibility of recording personal details, conversations, and photos. Many instances of assault \cite{1_russell_2014, 15_mashable_2014, 16_gross_2014} on wearers were also reported, resulting from a combination of privacy invasion and social tension\footnote{Google has come to represent gentrification in San Francisco ... [which] makes wearable device owners look and sound like one of the people whom residents of the city have come to feel oppressed by \cite{17_matyszczyk_2014}. The term ``Glasshole'' \cite{18_google_2015} has been defined specifically to refer to Google glass wearers.} . The public was generally unsympathetic to the situation, tweeting or commenting, ``I'm going to shove your pathetic nerd body into a locker,'' ``Nothing radicalizes you like having [your] home taken from you.'' and``As far as your 'hate crime' allegation is concerned, Entitled Tech Trash isn't a protected class just yet'' \cite{1_russell_2014,15_mashable_2014}.

{\color {red} This calls for privacy research in this area! It's more important than ever! Or something along those lines.}  To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices to prevent negative social impact and breaches of privacy. There has been extensive work on the need for showing users and bystanders how certain data is being captured so that they can have more control. We have an issue of showing everyone everything all the time, since attention is a finite resources. We need to identify situations that people want to warn them about, and transparently access things that are benign. A better understanding of users' risk perceptions will enable researchers and companies to focus on users' concerns. The goal of this paper is to gain a better sense of what those concerns are.
